% !TEX program = xelatex
% !TEX encoding = UTF-8 Unicode
% !TEX root = zys-cv-en.tex
\documentclass{cv_en}

%% basic personal info
\def\name{Xin Wang}
\def\phone{(+86) 13083675961}
\def\email{wangxinhhhhhh@gmail.com}
\def\LinkedIn{WxxW2002}
\def\github{WxxW2002}
\def\site{github.com/WxxW2002}

\begin{document}
\section{Education}
\institution{Shanghai Jiao Tong University}  \location{Shanghai, China}\\
\textit{B. Eng} in Information Security \ztime{Sept. 2020 --- Jun. 2024 (Expected)}\\

\begin{zitemize}
  \item \textbf{Grades Overall:} 89.6/100, 
        \textbf{GPA:} 3.87/4.3, 
        \textbf{Rank:} 6/89, 
        \textbf{CET6:} 556
  \item \textbf{Seleted A+ Courses:} 
        Programming Thought and Methods (Honors) (95/100),
        Information Theory and Coding (95/100) 
        and 15 others
  \item \textbf{Research Direction:} 
        Cryptography, Blockchain and Consensus Protocols, Privacy Computing; Application of Machine Learning in Cryptography and Cybersecurity
\end{zitemize}

\section{Experience}
\textit{Group Number}, Tutor: \textbf{Prof. Weidong Qiu} \ztime{Oct. --- Present}
\begin{zitemize}
  \item \textbf{Introduction:} This project is based on the requirements of various laws and regulations, combined with advanced artificial intelligence technology, to build automatic detection of illegal collection and use of personal information by App.
  \item \textbf{Expected Result:} Build an automated APP privacy detection platform to conduct automated compliance detection for apps in accordance with relevant laws and regulations.
\end{zitemize}

\textit{Group Number}, Tutor: \textbf{Prof. Dawu GU} \ztime{Mar. 2023 --- Aug. 2023(Expected)}
\begin{zitemize}
  \item \textbf{Introduction:} On July 5, 2022, NIST announced four post-quantum cryptography algorithms to be standardized to combat quantum computer attacks. This project will study previous work, propose possible new misuse attack methods, and form a software package to discover and verify possible misuse problems in future post-quantum cryptography software applications.
  \item \textbf{Expected Result:} Build a Misuse Problem Analysis Package for Standard Algorithms in Post-Quantum Cryptography.
\end{zitemize}


\section{Project}
\textbf{Sniffer-Wirecat}\enskip \underline{\href{https://github.com/ysyszheng/wirecat}{\faGithub}}
\begin{zitemize}
  \item A network sniffer based on the Qt platform, mainly written in C++ language. It is used to capture and analyze network traffic. The accuracy of its packet capture and analysis is close to mainstream software such as Wireshark.
  \item The bottom layer uses the Libpcap library to capture original network packets, and implements functions such as packet analysis, address, port number and protocol filtering, payload content search, IP fragment reassembly, and log recording.
\end{zitemize}

\textbf{SJTU Canteen Evaluation Website}\enskip \underline{\href{https://github.com/WxxW2002/SJTU-canteen}{\faGithub}}
\begin{zitemize}
  \item A canteen gourmet and evaluation website of SJTU. The front end uses HTML, CSS, JavaScript, and the back end uses the Django framework.
  \item This website realizes functions such as registration and login, popular recommendation, latest evaluation, search, graphic display, rating, etc.
\end{zitemize}

\section{Honors and Awards}
\begin{zitemize}
  \item Shanghai Jiao Tong University Zhiyuan Honor Scholarship(200 in total)\ztime{2020, 2021, 2022}
  \item "85th Computer Science Education Development Fund and Yang Yuanqing Education Fund"(8 in total)\ztime{2022}
  \item National Encouragement Scholarship for the 2020-2021 academic year (1\%)\ztime{2021}
  \item "Three Good Students" in the 2020-2021 academic year of Shanghai Jiao Tong University(Top 1\%)\ztime{2021}
\end{zitemize}

%\section{社团工作}
%\institution{800号电影社，上海交通大学}\\
%\textit{外联部} \ztime{2021年9月 --- 2022年8月}
%\begin{zitemize}
%  \item 负责活动场地的借用、租用及活动的签章，经费报销和拉取赞助.
%  \item 负责社团活动的组织、筹备与举办, 包括招新、社团展示等.
%\end{zitemize}

\section{Skills}
\begin{tabular}[t]{ll}
  \textbf{Programming Languages:} & C/C++, Python, HTML/CSS/JavaScript, Assembly (x86, ARM), MATLAB\\
  \textbf{Tech skills:} & GNU/Linux, Git, Vim, GDB, \LaTeX, Qt,  Pytorch\\
  \textbf{Personal Hobbies:} & Music, Movie, Gaming 
\end{tabular}

\end{document}